pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-28 article.tex
Show first ESSes

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Other examples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are many other examples that can be found in the \verb;pirouette; 
documentation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\centering
\begin{tabular}{ | r | l | l | l | l | }
\hline
\multirow{2}{*}{\textbf{Example}} & \multicolumn{2}{c|}{\textbf{True tree}} 
                                  & \multicolumn{2}{c|}{\textbf{Twin tree}} \\
\cline{2-5}
                                  & \textbf{HPD} & \textbf{range} & \textbf{HPD} & \textbf{range} \\
\hline
1  & $0.20$  & $0.0 - 0.27$  &         &               \\
2  & $0.02$  & $0.0 - 0.08$  &         &               \\
3  & $0.018$ & $0.0 - 0.1$   & $0.019$ & $0.0 - 0.11$  \\
4C & $0.22$  & $0.0 - 0.088$ & $0.009$ & $0.0 - 0.056$ \\
4G & $0.020$ & $0.0 - 0.075$ & $0.013$ & $0.0 - 0.052$ \\
\hline
\end{tabular}
\caption{Results of the examples. Errors are shows with the 
  highest posterior density first, and the range of the errors in
  round brackets second. Experiment 4 is split in two rows
  by either the candidate ('C') or generative model ('G') 
}
\label{tab:results}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Here we discuss how to interpret the results of \verb;pirouette;.
Figure \ref{fig:example_1} shows that the generative model 
gives an error distribution with a highest posterior density (HPD) 
\giovanni{probably "median" is a better word}
\richel{HPC is a valid Bayesian term I learned from the BEAST book}
at 0.02
\giovanni{I would increase the precision to the second significative digit, e.g. 0.017},
The range of errors goes from 0.0 to 0.27 
As we know the generative model, 
this error distribution is the minimum noise that BEAST2 produces 
for that generative model.
\richel{Show effective sample size}

@@

\giovanni{
  since you refer, for every RQ, to the same values, 
  it could be better to show them as a table
}

>>>>

An overview of \verb;pirouette;'s main functions is shown in 
table \ref{tab:functions}, which are all demonstrated in the examples
below.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\centering
\begin{tabular}{ | r | l | l | l | l | }
\hline
\multirow{2}{*}{\textbf{Example}} & \multicolumn{2}{c|}{\textbf{True tree}} 
                                  & \multicolumn{2}{c|}{\textbf{Twin tree}} \\
\cline{2-5}
                                  & \textbf{HPD} & \textbf{range} & \textbf{HPD} & \textbf{range} \\
\hline
1  & $0.20$  & $0.0 - 0.27$  &         &               \\
2  & $0.02$  & $0.0 - 0.08$  &         &               \\
3  & $0.018$ & $0.0 - 0.1$   & $0.019$ & $0.0 - 0.11$  \\
4C & $0.22$  & $0.0 - 0.088$ & $0.009$ & $0.0 - 0.056$ \\
4G & $0.020$ & $0.0 - 0.075$ & $0.013$ & $0.0 - 0.052$ \\
\hline
\end{tabular}
\caption{Results of the examples. For the true and twin tree,
  the highest posterior density (HPC) and range of the errors 
  is shown. Experiment 4 is split in two rows
  by either the candidate ('C') or generative model ('G') 
}
\label{tab:results}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Here we discuss how to interpret the results of \verb;pirouette;.
Figure \ref{fig:example_1} shows that the generative model 
gives an error distribution with a highest posterior density (HPD) 
\giovanni{probably "median" is a better word}
\richel{HPC is a valid Bayesian term I learned from the BEAST book}
at 0.015
The range of errors goes from 0.0 to 0.097 
As we know the generative model, 
this error distribution is the minimum noise that BEAST2 produces 
for that generative model.
We measure the effective samples as well, and all are well above
the recommended value of 200 \ref{drummond2015bayesian}, 
as shown in table \ref{tab:esses_example_1}.

\input{example_1_esses.latex}
% has label tab:esses_example_1

@@
